Carbonate chemistry at Ny-Ålesund

### 2023-05-29 awipev-CO2.Rmd
refined paths

#define who is the user and define path
#if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

@@

#export latex table
tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
```
**_Comparison of various formulations compared to Lueker et al. (2000)_**

@@

#export latex table
tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_at_ct.tex"))
```

>>>>

#define who is the user and define path
#if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
#if (Sys.getenv("LOGNAME") == "gattuso") path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"

# MacBook
if (Sys.getenv("R_PLATFORM") == "aarch64-apple-darwin20") {
  path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
  tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
#iMac Home
if (Sys.getenv("R_PLATFORM") == "x86_64-apple-darwin20") {
  path = "../../kDrive2/Documents/experiments/exp168_awipev-CO2/"
  tables_path <- "/Users/gattuso/kDrive2/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
# Samir
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

@@

#export latex table
knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
```
**_Comparison of various formulations compared to Lueker et al. (2000)_**

@@

#export latex table
knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_at_ct.tex"))
```
